---
title: "ScholarHistory.Rmd"
output: html_document
editor_options: 
  chunk_output_type: console
---

Playing with Google Scholar: from  http://fossilsandshit.com/research/metrics/

Install package and get my Google Scholar ID.
```{r}
#install.packages("scholar")
library(scholar)
```

Insert your Scholar ID here from your profile URL (eg https://scholar.google.co.uk/citations?user=P7FvGMEAAAAJ&hl=en)

## Department of Geography Faculty

Get google scholar ids.
```{r}
ID0 <- "uF8tRWQAAAAJ"  # Jim
ID1 <- "pwKHg7oAAAAJ" # Chris
ID2 <- "d4KNZWEAAAAJ" # Sarah
ID3 <- "NJgoH2YAAAAJ" # Victor
ID4 <- "WaiqcVcAAAAJ" # Mark
ID5 <- "bYJ86_kAAAAJ" # Tingting
ID6 <- "0pIuR1IAAAAJ" # Steph
ID7 <- "dLO_EsoAAAAJ" # Tyler
ID8 <- "4JSwERAAAAAJ" # Sandy
ID9 <- "I9AhwXAAAAAJ" # Sage
ID10 <- "brNaEAsAAAAJ" # Mabel
ID11 <- "S5HP8uEAAAAJ" # Bradford
ids <- c(ID0, ID1, ID2, ID3, ID4, ID5, ID6, ID7, ID8, ID9, ID10, ID11)
Names <- c("Elsner, James", "Uejio, Chris", "Lester, Sarah", "Mesev, Victor",
          "Horner, Mark", "Zhao, Tingting", "Pau, Stephanie", "McCreary, Tyler",
          "Wong, Sandy", "Ponder, Sage", "Gergan, Mabel", "Johnson, Bradford")
```

Citation history
```{r}
df <- data.frame()
for(i in 1:12){
  df0 <- get_citation_history(ids[i])
  df0$Name <- Names[i]
  df <- rbind(df0, df)
}

library(dplyr)

df = df %>%
  filter(year < 2020)

library(ggplot2)

ggplot(df, aes(x = year, y = cites, fill = Name)) +
  geom_bar(stat = "identity")  +
  scale_x_continuous() +
  scale_y_continuous(limits = c(0, 3000)) +
  xlab("") + ylab("Number of Citations") +
  theme_minimal() +
  ggtitle("Citations by Current FSU Geography Faculty\n [from Google Scholar]",
          subtitle = "Analyzed using the scholar package by James Keirstead")
```

Number of published papers.
```{r}
nPapers <- get_num_articles(ID0)
nPapers
```

Number of unique journals
```{r}
nJournals = get_num_distinct_journals(ID0)
nJournals
```

Number of "top" journals according to DE Acuna, S Allesina, KP Kording (2012) Future impact: Predicting scientific success. Nature, 489, 201-202. http://dx.doi.org/10.1038/489201a.
```{r}
nJournalsTop <- get_num_top_journals(ID0)
nJournalsTop
```

When did I become a scientist?
```{r}
get_oldest_article(ID0)
```

Get profile information
```{r}
profile <- get_profile(ID0)
```

Get publications and write to a csv file
```{r}
get_publications(ID0) %>%
#  filter(year >= 2010) %>%
  top_n(n = 10, cites) %>%
  arrange(desc(cites)) %>%
  select(cites, title, journal, year)
# write.csv(pubs, file = 'citations.csv')
```

Predict  h-index
```{r}
h.index = predict_h_index(ID0)
h.index
```

Compare scholars.
```{r}
df <- compare_scholars(ids)

df <- df %>%
  filter(year < 2020 & year > 1988) 

ggplot(df, aes(x = year, y = cites, color = name)) +
  geom_line() +
  theme_minimal() +
  ylab("Total Citations [Google Scholar]")
```

Compare scholar careers.
```{r}
df = compare_scholar_careers(ids)

df2 = df %>%
   group_by(name) %>%
   arrange(year) %>%
   mutate(total = cumsum(cites)) %>%
  filter(year < 2017)
  
ggplot(df2, aes(x = year, y = total, color = name)) +
  geom_line() +
  scale_x_continuous(breaks = 1984:2016) +
  theme_minimal() +
  ylab("Total Citations [Google Scholar]")
```

## College of Social Science and Public Policy Faculty

Get the data from a spreadsheet. It was emailed by Deana Rohlinger on March 2, 2020. I posted it on Google Sheets and added the Department names. Here I import the data and remove rows with a missing ID.
```{r}
College.df <- read.csv(file = "Faculty Google Scholar ID.csv", header = TRUE,
                       stringsAsFactors = FALSE) %>%
  dplyr::filter(ID != "") %>%
  dplyr::filter(Name != "James Wright") 
#  dplyr::filter(Department == "Geography")
```

Get citation history from google. Note: There maybe a limit on how many times you ping google.
```{r, eval=FALSE}
df <- data.frame()
df0 <- data.frame()
for(i in 1:nrow(College.df)){
  print(i)
  df0 <- get_citation_history(College.df$ID[i])
  df0$Name <- College.df$Name[i]
  df0$Department <- College.df$Department[i]
  df <- rbind(df0, df)
}

write.table(df, file = "CollegeLevelData.txt")
```

Plot
```{r}
df <- read.table(file = "CollegeLevelData.txt", 
                 header = TRUE)

df2 <- df %>%
  dplyr::filter(year < 2020 & year >= 1995) %>%
  dplyr::group_by(year, Department) %>%
  dplyr::summarise(TotalCites = sum(cites))


ggplot(df2, aes(x = year, y = TotalCites, fill = Department)) +
  geom_bar(stat = "identity")  +
  scale_x_continuous() +
  scale_y_continuous(limits = c(0, 15000)) +
  xlab("") + ylab("Number of Citations") +
  theme_minimal() +
  ggtitle("Citations by Current College Faculty\n [from Google Scholar]")

```